Viscous Transport in Eroding Porous Media

### 2019-08-20 docs/transport/erosion_transport.tex
add a new figure in transport paper

\begin{figure}[H]
%\caption{\label{fig:Eroding20anomalous} The
%mean squared displacement of the tracer trajectories  at several
%different stages of the erosion process.  As the porosity increases, the
%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
%}
\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
diffusion in 20 nearly touching bodies with respect to six porosities
and the reference line of 100\% porosity.  The first moment (left) is
the mean length of streamlines and the second moment (right) is the }
\end{figure}

>>>>

\begin{figure}[H]
%\caption{\label{fig:Eroding20anomalous} The
%mean squared displacement of the tracer trajectories  at several
%different stages of the erosion process.  As the porosity increases, the
%mean squared displacement tends towards $\sigma^2_\lambda(t) \sim t^$
%}
%\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\center
\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment_long}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
diffusion in 20 nearly touching bodies with respect to initial porosity (37.68\%) and another six porosities
during the eroding. The dashed line correspondes to a porosity of 100\% and the dashed-dotted line is a 
line of best fit with slope 0.5742.}
\end{figure}
